---
title: "Exploring the lost parties of Pre-revolution era Russia"
author: Iz Leitch
thanks: "Code and data are available at: [FILL IN LATER]"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "This paper explores the legacy of different political groups in pre-revolution Russia. It takes the data from UCLA's Social Science Data Archive Dataverse and examines the different party affiliations, their membership counts, and the amount of time people spent in these parties. It finds possible connections between minor factions and parties in the dataset, and shows evidence in favour of a more rich explanation of the formation of the Soviet leadership. This data and what can be gleaned from it is not only useful for Slavic Studies, but also in contextualizing modern politics, as the data shown here displays a clear developmental pattern as ideas from the 1800s recur and inform that period of the early 1900s, so does the 1900s inform us in the present day."
format: pdf
number-sections: true
bibliography: references.bib
editor: 
  markdown: 
    wrap: 72
---

```{r}
#| include: false
#| warning: false
#| message: false
library(tidyverse)
library(dplyr)
library(scales)
library(ggplot2)
library(here)
library(readr)
```

```{r}
#| include: false
#| warning: false
#| message: false
graphing_values_cleaned <- readr::read_csv(here::here("inputs/data/graphing_values_cleaned.csv"))

graphing_values_cleaned$political_party <- reorder(graphing_values_cleaned$political_party, graphing_values_cleaned$time_spent_in_party.count)

graphing_membership_ambiguous <- readr::read_csv(here::here("inputs/data/graphing_membership_ambiguous.csv"))


```

# Introduction

What do we really know about the Russian Revolutions?

In this paper, using the UCLA Soviet Data Bank and crossing referencing
the party ids with the party membership dataset, a deeper understanding
of the complex social and political dynamics of Pre and Early-Revolution
Russia can be gained beyond the simple Reds vs Whites, and Bolsheviks vs
Mensheviks narratives that are so often called on when aiming to explain
the political climate.(sec-background) gives us the foundation to
understand the major and minor players as is traditionally understood in
Slavic Studies, such that we can validate or invalidate these narratives
with the data presented. In the Data portion, this paper looks at all
the listed parties inside the dataset as a whole, comparing the amount
of people in each party, and the average duration they spend with it. In
the discussion of the data, we explore the limitations of the data, and
the political implications. Lastly, Next Steps looks toward the future
and what else can be done with this information and data.

# Background {#sec-background}

The formation of the Soviet Union is often portrayed in simplistic ways,
which is in some ways understandable due to the distance both physical
and temporal we have from the event, yet for those interested in the
Slavic Studies field the Russian Revolution is hugely important not just
for Russian Studies, but the whole of Slavic Studies as it greatly
changed the social and political landscape of multiple nations covering
multiple ethnic groups, age groups, politically affiliated groups and
more. While in Canada where this paper is being written, most might only
know about Stalin, Lenin and Trotsky from reading Animal Farm in Grade
10 there is much more to understand about the situation. But coming back
to that distance, it might be easy to ask why should I, presumably
someone who has no Slavic background and doesn't plan on visiting any
time soon, care about the inner workings of 1900s era bureaucrats and
their political affiliations? And to that I might say that one need only
turn on the news to see the continued effects of the Soviet Project's
legacy. The mindsets that go into these political parties, no matter how
small, often have reverberating effects throughout history, and in ways
that some seek to shut down, as we will soon discuss in Political
Repression, and Nationalism. But even if Grade 10 History class or its
equivalent has now passed into the realm of history itself, have no
fear, here is a quick run down on the common story taught about the
Revolution.

## timeline {#sec-timeline}

The common story begins with the Tsar and Lenin. Prior to the Soviet
Union, Russia was headed by an all powerful Tsar and his all powerful
family the Romanovs. And they were very powerful, an earlier revolt in
1825 the Decemberist Revolt (the one that caused Dostoevsky to be the
way he turned out) was held to shift more power away from the Tsar into
the hands of the Russian Elite. This revolt was squashed, and the elites
who took part were sent to Siberia in exile if not outright killed.
Forty-ish odd years later in 1861 serfdom, a form of slavery was
overturned, giving the peasantry the ability to not be bought and sold,
yet many of them still lived in squalid conditions. For comparison,
England abolished serfdom in around 1574, and American Chattel Slavery
would be abolished 4 years later by the 13th amendment in 1865. So as
far as timelines are concerned, the end of serfdom was very recent to
the Revolution. Though to be more exact it there were multiple
revolutions. The first one isn't often discussed, but is useful to know
about, the Bloody Sunday or First Revolution in 1905. This revolution
would lead to the slaughter of around 200 workers (Clodfelter) with the
number only going up in the following months and then years leading up
the February Revolution.

The February Revolution is next Revolution that makes up "the Communist
Revolution" happening in March of 1917 (sidenote: The February
Revolution happened in March because Russia used a different calendar at
the time). This would lead to the Death of the Tsar and the formation of
an early government, not one long for this world however as in November
of that same year the October Revolution would begin, launching a Civil
War not resolved until 1923. This may lead one to wonder, why would
there be so many revolutions in "the Revolution" and who were these
groups fighting in the Civil War? This would be due to the topic of
today's paper, the many parties and factions inside the Russian and more
broadly Eastern-European political world. The Civil War can also be
called the Reds vs Whites, though that too is an oversimplification. The
Reds as we will soon see in Data had multiple smaller factions within
it, but largely represented the overthrow of the Tsar, with the Whites
then being the Tsarist party, but that still doesn't explain the
February and the October revolution. That, dear reader, was the toss up
between the Mensheviks and the Bolsheviks.

this explains the timeline, and the reds vs whites

## Mensheviks and Bolsheviks {#sec-mensh-bolsh}

If you have bothered to read this far, you may already know about the
Mensheviks, however you almost certainly know about the Bolsheviks and
that is due to the changing landscape of power between March 1917 and
November 1917. Together the Menshevik and Bolshevik parties combined to
be the "Reds", both working to change the rule of the Tsar over to the
people. However a lot can be gleaned about the balance of power within
the Revolution simply by understanding the names. Bolsheviks, named
after bolshinstvo, or majority, literally formed the majority coaliation
in the Red Revolution, lead by Lenin they became the winners of the
October Revolution and the rest is history, however their little brother
party, the more moderate Mensheviks -from menshinstvo literally
minority, had their own role to play, even outnumbering the Bolsheviks
at certain points in time. However these two parties are as far as one
is likely to have heard about the proto-Revolutionary parties, something
that this paper seeks to correct, with a look at 55 different factions
and their memberships histories and records.

# Data {#sec-data}

In the paper I run our analysis in `R` [@citeR], with the much needed
help from other packages such as 'readr' [@cite-readr], 'here'
[@cite-here], 'tidyverse'[@cite-tidyverse], and 'dplyr' [@cite-dplyr].
With ggplot [@cite-ggplot], the data can be better visualized in the
form of graphs.

The data seeks to look at the different political affiliations of
bureaucrats in the Russian Government prior to 1923. Bureaucrats because
that is what the data set is limited to, and because Russian and Soviet
Union data set showing anything other than economic output are
incredibly hard to find, and often broken up in such a way that it
becomes hard to navigate. For example the primary data set in this
paper, the parstazh data from UCLA {@cite-UCLA} is only navigable due to
the presence of another data set at UCLA, the party codes data set,
which has the reference key to the 55 parties allowing someone to
actually know what all 55 actually reference. Last to understand before
diving in is the nature of the data. Due to being a dataset from
someone's personal references, from around 100 years ago, originally in
another language, originally from a highly repressed country and region
prone to hiding or outright destroying anything that they disagreed
with, it is very difficult to gain a full understanding of what might be
lost, or even destroyed about the data. The graphs I work with try to
take data with the least missing, and then the least relevant data
missing, but data missing is a major issue so it is important to keep
that in mind while reading.

```{r}
#| label: fig-1
#| fig-cap: Average Time Spent In Each Party for Parties with Greater than One but Fewer than Ten Members
#| fig-width: 8
#| fig-height: 4
#| echo: false
#| warning: false
#| message: false
## this sets the colour palette for the bar graphs
colors <- c("black", "lightgrey", "blue", "green", "yellow","orange", "red") 
breaks <- c(2, 4, 6, 10 ,20, 30, 40, max(graphing_values_cleaned$time_spent_in_party.count)) 
palette <- colorRampPalette(colors)(length(breaks)-1) 
names(palette) <- c("black", "lightgrey", "blue", "green", "yellow","orange", "red") 

## this splits the graphs so they can be more easily understood
graphing_values_cleaned_one_to_sixteen <-graphing_values_cleaned[order(graphing_values_cleaned$political_party)[1:16],]

## this graphs all the parties with on average less than one year of participation
ggplot(graphing_values_cleaned_one_to_sixteen, aes(x = political_party, y = time_spent_in_party.mean, fill = time_spent_in_party.count))+geom_bar(stat = "identity", width = 0.6) +
  labs(title = "Average Time Spent In Each Party for Parties with Memberships \n Greater than One but Fewer than Ten Members",
       x = "Parties",
       y = "Average Time Spent in Each Party by Years")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1),legend.margin = margin(75,0,0), legend.key.height = unit(1.25, "cm"),legend.title.align = 0, legend.title = element_text(angle = 0, vjust = -0.2, hjust = 3), plot.title = element_text(hjust = 0, margin = margin(b=40)), axis.title.y = element_text(angle = 90, vjust = 0.5, hjust= 0.8))+
  scale_fill_gradientn(colors = palette, breaks = breaks, limits = c(0, max(graphing_values_cleaned$time_spent_in_party.count)), name = "Number of Party Members")
  
```

To better understand the data, it has been separated into smaller more
manageable chunks. Let's take (@fig-1). We can see that even in
political groups with few recorded members that there is still a
significant time commitment at hand, with several of these minor parties
having membership lengths over 5 years. This is even more true for when
we look single member parties with one clocking in at over 92 years
spent with that political affiliation.

```{r}
#| label: fig-2
#| fig-cap: Average Time Spent In Each Party for Parties with Greater than Ten Members
#| echo: false
#| warning: false
#| message: false
#| fig-width: 8
#| fig-height: 4
## this sets the colour palette for the bar graphs
colors <- c("black", "lightgrey", "blue", "green", "yellow","orange", "red") # Define the colors for the gradient
breaks <- c(2, 4, 6, 10 ,20, 30, 40, max(graphing_values_cleaned$time_spent_in_party.count)) # Define the breaks for the values
palette <- colorRampPalette(colors)(length(breaks)-1) # Create the color palette
names(palette) <- c("black", "lightgrey", "blue", "green", "yellow","orange", "red") # Assign names to the palette colors

##this separates the values for parties with a significant amount of members
graphing_values_cleaned_seventeen_to_twentysix <-graphing_values_cleaned[order(graphing_values_cleaned$political_party)[17:26],]
##this graphs the parties with more than one average year of participation
ggplot(graphing_values_cleaned_seventeen_to_twentysix, aes(x = political_party, y = time_spent_in_party.mean, fill = time_spent_in_party.count))+geom_bar(stat = "identity", width = 0.6) +
  labs(title = "Average Time Spent In Each Party for Parties with Greater than Ten Members",
       x = "Parties",
       y = "Average Time Spent in Each Party by Years")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1),legend.margin = margin(75,0,0), legend.key.height = unit(1.25, "cm"),legend.title.align = 0, legend.title = element_text(angle = 0, vjust = -0.2, hjust = 3), plot.title = element_text(hjust = 0, margin = margin(b=40)), axis.title.y = element_text(angle = 90, vjust = 0.5, hjust= 1))+
  scale_fill_gradientn(colors = palette, breaks = breaks, limits = c(0, max(graphing_values_cleaned$time_spent_in_party.count)), name = "Number of Party Members")

```

Interestingly, in @fig-2 against common understanding the most complete
data ofthe dataset shows strongest turn out for a group called RSDRP,
followedby the Mensheviks, the Mensheviks again in the form of the
Social Democrat Internationalists and then the Bolsheviks, the Socialist
Revolutionary, Social Democratic Party (non-RSDRP), Mezhduraionsty,
Jewish Bund, Pre-Social Democratic Party and the Left Socialist
Revolutionary Party. By taking these top parties in terms of
participation, we can see that significant Left Political involvement in
the group surveilled to make this dataset. So what are the Parties at
hand? We've covered two of them, the Bolsheviks and the Mensheviks in
@sec-mensh-bolsh, but that first group the RSDRP is the party prior to
the split that gives the Bolsheviks and Mensheviks their name in 1903.
Because this dataset appears to have larger turn out for the RSDRP when
in fact due to the way the data is gathered, individuals under
surveillance can be in multiple parties, just at different times,
something that is reflected in this statistic.

More factionalism is at play with the next uncovered party the
Menshevik/Social Democratic Internationalists Party. Preliminary
research, that being what can be sourced without significant translation
or emailing a Slavic Studies Professor about it, shows two parties under
the Internationalists title, the Russian Social Democratic Party (of
Internationalists) and the Menshevik Internationalists. It is unclear
which of the two this is referring to, but the Menshevik
Internationalists are a left-leaning faction within the Menshevik Party,
and the Russian Social Democratic Party (of Internationalists) are
themselves a splinter group of that faction. This is interesting because
the RSDPoI as I will call them, had connections to the newspaper Novaya
Zhizhn, which is the name of another party further down the line in
terms of membership. Implying that the Novaya Zhizhn party is actually
RSDPoI and the Social Democratic Internationalists are the Menshevik
Internationalist. Slowly contextual research begins to unravel the
mysteries at the heart of this data set. So exciting!

Moving further down the list we have the Socialist Revolutionary Party,
and its many factions later to come as well. The Socialist
Revolutionaries were based in agrarian socialist thought. In the Russian
context they are the successors to the Narodnik movement, a movement
dedicated to protecting the unique relationship the Russian rurality had
with the land. For Slavic Studies students the name might ring a bell,
as the Narodniks come after Herzen's work, Herzen being the one to
publish the famous (in Slavic Studies circles at least) Who is to Blame
Paper? and being a key thought leader in the formation of Slavic
national identities. Remember earlier, in @sec-background, I discuss the
at the time extremely recent dissolution of serfdom? That is what lays
the background for this unique land-people relationship fo the Narodnik
movement, which gives way to the Socialist Revolutionary Party. This
party along with the at the time RSDRP oppose the interim government put
in place by the February Revolution, and like the RSDRP split into two
factions, in the case of the Socialist Revolutionaries that would be the
Right and Left Socialist Revolutionaries respectively.

Next we have the party that is the most exciting for me personally, the
Mezhduraionsty party. This party has no external evidence outside of
this data set of ever existing, which is more thoroughly discussed in
the Data Limitations portions. This party could also be incorrectly
latinized, a possibility I raise only due to the closeness of
Mezhduraionstry to Mezhdunarodnyy. This is important because
Mezhdunarodnyy or Internationalism has already been raised by other
parties as a significant issue, on the other hand the way it is
latinized now Mezhduraionsty, Inter-district party, raises the idea of
district factionalism being at play within the larger parties, however
that would be difficult in the least to impirically substantiate as this
data set is biased toward a Moscow perspective so other district
perspectives are limited.

Next on the list is the Jewish Bund, who also have their own
significance. Unbeknownst possibly, to those in the west is the
significance of Judaism to Russia and the Soviet Union. Originally
proclaiming to protect the rights of its Jewish citizen in part due to
the large active Jewish Socialist Bund. Of course later this group would
be dissolved during the Civil War and its attempts to assimilate smaller
factions within itself, leading to many a negative outcome too graphic
to discuss here, but an important party nonetheless.

Last in line is the Left Socialist Revolutionaries, already discussed as
a faction of the Socialist Revolutionaries, and the Pre-Social
Democratic Party which is lost to time along with the Mezhduraionsty
Party.

```{r}
#| label: fig-3
#| fig-cap: Membership of the 55 parties Inclusive of Ambiguous leaving dates
#| echo: false
#| fig-width: 8
#| fig-height: 4

graphing_membership_ambiguous$political_party <- reorder(graphing_membership_ambiguous$political_party, graphing_membership_ambiguous$number_joined)

## this shows the number of people joining each party inclusive of individuals with ambiguous leaving dates
ggplot(graphing_membership_ambiguous, aes(x = political_party, y = number_joined))+geom_bar(stat = "identity") +
  labs(title = "Membership of the 55 parties Inclusive of Ambiguous leaving dates",
       x = "Political Party",
       y = "Number of People Joined")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "right")

```

Now @fig-1 and @fig-2 may have looked at the more complete data, those
with complete parties, start years and end years, but it is in the more
ambiguous data that we can really see the truth. Where @fig-2 shows few
participants in Bolshevik movement, @fig-3 shows the divide between that
party leading up to the Revolution and all the others. This is likely
due to the Bolsheviks winning the October Revolution so to speak and
coming out ahead of the other parties that it became specifically hard
to place an end year on people's involvement, as that is what this data
looks at, member involvement regardless of year left.That being said,
this still shows the involvement of the parties discussed above, the
Mensheviks, Pre-Social Democratic Party, Mezhduraionsty Party, RSDRP,
RSDPoI, and Jewish Bund, with a new group the SDKPiL, or Social
Democracy of the Kingdom of Poland and Lithuania, rising in membership
count to join the top 10 in terms of membership. Notably this party seen
in @fig-1 is unique due to it's long term commitment to the party,
averaging around 15 years spread over just under 10 members.

# Model {#sec-model}

We can model the difference in memberships inclusive of ambiguous data
with an exponential growth equation. However I will be honest, if you
have read this far you can probably tell that I'm not that good at math.
The Exponential Equation is as follows, where $x_0$ is the starting value, so I assume 1 in this case, r is the rate of growth and t is the discrete changes.
$ x_{t}=x_{0}(1+r)^{t}$

Exponential growth is useful for understanding the sheer size difference of the participation, and closely aligns with the dramatic change in participation across the 55 parties. 

# Results

The results of this investigation into the political participation of
Early 1900s Era Russia show a strong lineage of political thinking over
the many splinter factions arising from the February and October
Revolutions.

# Discussion {#sec-discussion}

## Data Limitations {#sec-data-limit}

Of course, we must discuss the limitations of this dataset, and there
are quite a few. After all for all the hard work that has been put in
the nature of data across so many boundaries, many of which were not as
open as they are today and many which are closing up again, there is
only so much that can be done to get workable data. One of these
unavoidable issues is the issue of translation. Due to the alphabet
difference, that being the difference between Cyrillic and Latin
characters, the names of certain parties are not perfectly preserved,
instead latinized. Latinization isn't wholly a bad thing but the use of
translation is inconsistent across the data, parties like Novaya Zhizhn
are left latinized but untranslated where other parties like the Left
Social Revolutionary Party is translated. This creates confusion and
leaves room for error. It also makes it difficult for English speakers,
at whom this data is targeted for to understand the political
implications of each Party. A party like Novaya Zhizhn makes sense only
if you know enough Russian to translate it, but the dataset isn't
primarily for a Russian speaking audience, most of the names of parties
are fully translated, so there is the loss of context on that one.

More egregious is one of the more populated parties in this dataset.
Even making it to the top 10 populated parties in the less ambiguous
data, the Mezhduraionsty party leaves behind no traces under that name
in English or in Russian. This leaves open the potential for it being
incorrectly latinized, or that the history of this party, in its state
now loosely translated to the inter district party, but this doesn't
bring up anything either. However if it was translated into English like
the other parties, that could take away the potential for latinization
errors, for example, before getting an amalgamated translation of inter
district party, I considered this an incorrect latinization for
mezhdunarodny party, or international party. Both of these have wildly
different implications for the dataset, yet because it's not in Cyrillic
or translated neither can be fully accepted or ruled out. Translating
these parties could even be an interesting place to explain the naming
behind such party. Instead this party is almost entirely lost and
forgotten about, only referenced in this dataset and no-where else
online in English or Russian.

Another interesting quirk of the data would be the inconsistent use of
nicknames and abbreviations for parties. In this category we can see
SKDPiL and the Kadets, respectively the Social Democracy of the Kingdom
of Poland and Lithuania and the Constitutional Democratic Party
respectively. While the nicknames can be useful for taking down the
information, in a list with so many parties lost to time completely, the
use of nicknames and abbreviations means that this data is likely to get
harder to understand for future generations, limiting possible
understanding. Also the abbreviations and nicknames give no explanation
for the actual party politics behind them, where Social Democracy of the
Kingdom of Poland and Lithuania, and Constitutional Democratic Party
both hint at those policies and what makes them interesting as parties.

### Bias in Sample {#sec-sample-bias}

Of course key to discussing the data is discussing how it was gathered.
While the data here is plentiful it only looks at a specific group in
pre revolutionary Russian society, that of the low level bureaucrat,
subject to political surveillance. Obviously, as the Russian Revolutions
are people's Revolution the lack of representation for the working and
agrarian classes is a highly felt loss. The lack of this is impossible
to understate for the issue of Political Representation in early 1900s
Era Russia.

Another element of bias in the data is again in the sample, with the
whole of the UCLA Soviet Data Bank being taken largely from the files of
Vsia Moskva (Seeing Moscow/Watching Moscow), this means that it is
highly biased towards the goings on of Moscow in particular, leaving out
and minimizing the impact of other vibrant cultural centers in Russia
like St.Petersburg, Novgorod, and the impacts of Rural thought in the
more distant districts. This also means it has a strong national bias,
as will be discussed in the Nationalism section. While that isn't
necessarily an issue as this paper looks at the issue of Political
Participation from a Russian Standpoint, it contributes to the continued
and ongoing erasure of Ukraine from Eastern European history and thought
as a whole.

### Missing Data {#sec-miss-data}

Missing Data is second only to Sampling Bias in terms of what plagues
this data. Of course we have gone over the parties with no recorded
history outside this data set, but there are likely parties recorded in
history not represented here due to time, and the inevitable loss of
information that comes with it, as well as due to the many challenges of
translation and naming discussed within @sec-data-limit. The problem
with missing data is that it cannot be filled in. Like with the
ambiguous leaving dates in @fig-3, we can only speculate as to what
might be the reason for that missing data, if we can tell it is there at
all. A key one that I can speak to based on my time with Slavic Studies
Scholar and Kiyvenite himself Professor. Koznarsky is the lack of
Ukrainian representation in the data set. This lack is keenly felt
because prior to the Ukrainian-Soviet war there was a short lived
Ukrainian People's Republic, autonomous separate from the soviet union.
This lack is so important now because the eventual fate of the Ukrainian
Peoples Republic was losing autonomy to Russia in the form of
Ukrainian-Soviet war, and due to the erasure of Ukrainian Socialism and
Socialists as a whole, many who opposed losing their national autonomy.
Instead the common narrative shows a strong and decisive Soviet Union
sweeping in and overtaking the last of Tsarist Supporters in Ukraine,
when that is simply not the case.

## Nationalism {#sec-national}

Another prevailing theme of the data is nationalist sentiments and
nationalism. Nationalism in Eastern Europe was fairly new at the time as
the concept of nationhood and nationality spread to slavdom in the late
18 early 1900s. Out of the 55 listed parties x of them directly
reference a specific country as a uniting theme. This tendency toward
nationalism becomes a key theme as the early soviet union spread out of
russia, conquering and absorbing nearby countries and ethnic groups in
its own nation building project. Yet the largest parties the Bolsheviks
and Mensheviks have no explicit ties to any nation. This lack of
national thinking isn't lack of national thinking, but rather the
formation of a new nation in the making the Soviet Union, one that would
necessitate breaking up and absorbing the national identities of the
countries it would absorb during the Civil War.

The lack of Ukrainian nationalism on a list that includes other
nationality based parties is particularly striking due to the rise in
desire for Ukrainian autonomy in the form of the Ukrainian peoples
republic and due to Ukraine's history of being subsumed by the Russian
narrative. It is then worth speculating whether that lack of presence in
this data is accidental or if records were erased as was commonplace
during the time of the Soviet Union. After all while we are looking at
data from the pre Soviet period we are living in the post Soviet period
and are unable at the moment to fully know the depth and breadth of what
has been lost or intentionally destroyed during that time.

## Longevity

Another prevailing theme of the data is nationalist sentiments and
nationalism. Nationalism in Eastern Europe was fairly new at the time as
the concept of nationhood and nationality spread to slavdom in the late
18 early 1900s. Out of the 55 listed parties x of them directly
reference a specific country as a uniting theme. This tendency toward
nationalism becomes a key theme as the early soviet union spread out of
russia, conquering and absorbing nearby countries and ethnic groups in
its own nation building project. Yet the largest parties the Bolsheviks
and Mensheviks have no explicit ties to any nation. This lack of
national thinking isn't lack of national thinking, but rather the
formation of a new nation in the making the Soviet Union, one that would
necessitate breaking up and absorbing the national identities of the
countries it would absorb during the Civil War.

# Next steps {#sec-next-steps}

Here is where we look toward the future, hopefully a better, more
nuanced one, and what else can be done with the data. In this paper I
allude to the possibility of the Mezhduraionsty party existing due to
possible district bias in the Menshevik and Bolshevik Parties, and I
discussed how this would be hard to do with the data at hand and its
Moscow bias, that being said the original data set does include Province
joined and Locale joined with only one issue, and it is a major issue.
Like the party tracking in the original data set, the Province joined
and locale joined values are all stored as numbers, with no clear code
for what those numbers are referring to. I'm sure with thorough enough
cross-referencing a hypothesis as to what those Provinces and locales
are could be made, likely using Zipf's law or something similar.

Furthermore work into discovering what the Mezhduraionsty party actually
refers to and what they did would open up new avenues into understanding
Socialist factionalism in the early 1900s period, but would likely
require a plane ticket and a lot of time to go through the archives of
that period, many of which are currently in Russia and inaccessible.

Lastly, for further development, using these parties to draw out
political lineages would be very interesting, and help illuminate the
way that these parties shape and continue to shape one another.

As well, with Slavic Studies there is always further reading to be done.
For those reading this paper and not writing it, here is a suggested
further reading to enhance your nuanced thinking on Soviet Politics
beyond the Red-Scare level thinking often perpetuated about this period.

## Further Reading

I recommend Isaac Babel's Red Calvalry for greater understanding of the
Civil War and the Bolshevik Perspective. As well Babel while he was
alive was Jewish and wrote another group of short stories often
collected with Red Calvalry called Tales from Odessa, Odessa being a
city with a strong Jewish history in Ukraine. His life and works shed
light on the Jewish experience of the Revolution, the good and the bad.

On the other hand, this paper almost entirely discusses the Left side of
the Revolution, as that was what was largely being surveilled for, on
the other hand to learn more about the Whites first hand, Mikhail
Bulgakov's White Guard shows the political tension in Ukraine during the
Civil War from the perspective of a Tsarist supporter as Bulgakov was
when he was alive. It closely takes from his own personal life and while
it isn't beating his magnum opus The Master and Margherita, it certainly
has it's own merit.

For understanding Narodniks, who lead into the Socialist Revolutionary
Party, I already mentioned Herzen, but Herzen's Who is to Blame? is
highly significant in the development of Socialist Agrarian philosophy,
with some even going on to say he is the father of Socialism.

Moving forward in time to the present, Kristen Ghodsee's Red Hangover is
an excellent work covering our Post-Soviet Perspective and shines a
light on why not everyone is pro-capitalism in ex-Soviet countries.

And if we want to go into the past and the future at the same time,
little remembered now but foundational at the time Bogdanov's Red Star
which outlines life on Communist Mars is useful for anyone looking back
through the bloodshed and murder of the Soviet Union who's thinking, why
would anyone ever want that? Well, they didn't want the bloodshed, and
the Bogdanov's dreams of a post-gender, post-money, post-space travel
society shine a light on what people were beginning to believe was
possible at the time, with Bogdanov himself being a key early communist
figure worth looking into.

# Conclusion

In conclusion, a lot can be learned from this

# Acknowledgements

I would like to acknowledge the hard work of the people at UCLA for
putting these and many more interesting Soviet and Pre-Soviet Era
datasets together, and Harvard for hosting them in such a way that
wayward Canadian Slavic Studies students such as myself can access them.
When it comes to Soviet material the instinct is often to keep it
hidden, but fighting against that instinct is much appreciated. I would
also like to acknowledge the work of Professor. Koznarsky for teaching
Kyiv: the City of Saints and Sinners which is where my knowledge of the
Ukrainian People's Republic has come from, as of most of my knowledge
about Ukraine, and Professor. Obradovic who taught the Slavic
Civilizations course when I was there which informs my understanding of
the development of national identity among the Slavic people circa the
early 1900s. Last of the Professors but certainly not the least, this
paper exists entirely in due to the hard work of Professor. Alexander,
otherwise the author would not know enough R for this to exist. All
Professors can currently be found at the University of Toronto.

On the other hand, less intellectually I will fess up and acknowledge
Wikipedia for helping me find any evidence of many of these parties even
existing. Google, for being the central repository of information I used
to confirm things have no evidence of existing, and ChatGPT for bouncing
code ideas off of when no one else is around. \newpage

\appendix

# Appendix {.unnumbered}

# Additional details

List of all 55 parties and what they are about:

1.  Bolsheviks: This is the majority party when talking about Revolution
    Era politic. A more extreme party helmed by Vladimir Lenin. They
    would lead the October Revolution and the formation of the Soviet
    Union

2.  Mensheviks: The minority party to the Bolsheviks majority. More
    moderate.

3.  Populist:

4.  People's Will: Left-wing terrorist group which conducted
    assassinations in attempt to overthrow the Tsar.

5.  Socialist Revolutionary: Building from the Narodnik movement, the
    represent agrarian Socialism and were a fairly large party.

6.  Right Socialist Revolutionary: Half of the split when the Socialist
    Revolutionary Party broke up.

7.  Left Socialist Revolutionary: The other half of the split.

8.  Anarchist:

9.  Mezhduraionsty: Discussed above, but this party has no evidence of
    ever existing. However it is the top 10 of the 55 parties listed in
    terms of membership. It really makes you wonder what has been lost,
    or if it was lost in translation. Though my Russian is only
    intermediate, preliminary searches in Russian also yield no results,
    however, it is possible that this is actually supposed to say
    mezhdunarodny party, which would make more sense, mezhdunarodny
    being the word for international, making this the international
    party. That being said this only speculation, neither interpretation
    yield any useful results or historical evidence to their existence.

10. Kadet: The Kadets, fro K-D a shortening of Constitutional Democratic
    Party, had a more significant role in politics than this data-set
    would suggest, though their absence is fascinating nonetheless. This
    party was significant in the in-between government between the
    February and October Revolutions, and by early research findings
    appears to be largely positive toward maintaining the autonomy of
    the different factions and ethnic groups.

11. Pre-Social Democratic: No evidence of this one.

12. RSDRP (joint-group): This is the party that the Bolsheviks and
    Mensheviks originate from.

13. Social Democratic (non-RSDRP):

14. Dashnaktsutiun Party: Armenian Nationalist Party

15. League of Lithuanian Workers: A nationalist workers party,
    specifiying in Lithuainians

16. Anarchist-Communist:

17. Proletariat Party (Poland): What it says on the tin.

18. Anarcho-Syndicalist:

19. Polish Socialist Party: A nationalist socialist party, this time for
    Poland.

20. SDKPiL: Stands for Social Democracy of the Kingdom of Poland and
    Lithuania, so nationalist again. This one would cease operations
    in 1918. 1918 being significant due to being in the middle of the
    Civil War and also during the Ukraine-Soviet War. During this time
    there is a lot of Soviet expansion into otherwise sovereign nations.

21. Menshevik/Social Democrat Internationalists: This one seems to be a
    Menshevik splinter group, and the presence of Social Democrat
    Internationalists on this list furthers the theory of the
    Mezhduraionsty party actually being the Internationalists party.

22. Latvian Social Democrats:

23. Borot'sbisty: This party also has no evidence it ever existed, and
    my Russian knowledge in this case hasn't helped find any possible
    alternatives either. Side note: don't look this one up in public.

24. Jewish Bund: This group is highly significant.

25. Trudoviki (Labour Group): Another Agrarian Socialist party, this one
    had influence in the February Revolution interim government, before
    being ousted.

26. Lithuanian Social Democrats: Yet more nationalist parties.
    Lithuanian again this time.

27. Popular Socialist Party: Not that popular as evidenced by the data.

28. Gummet:

29. Communist Workers Party of Poland:

30. Young Bukhara Party:

31. Edinstvo Group:

32. Rumanian Social Democratic Party:

33. Social Democratic Amalgamationists:

34. Socialist Revolutionary Maximalists:

35. Menshevik Defensists:

36. Polish Communist Party:

37. Rabochie Znamia:

38. Zemstvo Movement: A Zemstvo is something you may know about if you
    read Anna Karenina. The Zemstvo's were the small local governments
    often focused on agriculture and represented a sort of pre-modern
    thinking. Also pro-serfdom thinking depending on the time period.
    This inclusion is interesting because while the Zemstvo's no longer
    had the same importance as under serfdom, the party still existed.
    It goes to show the way that past political movements continue to
    affect the present.

39. Legal Marxists: named from their role in legal publications.

40. British Socialist Party

41. Workers and Peasants Socialist Party: probable mistranslation, the
    only Workers and Peasants Socialist Party is from France in the
    1930s, so either this party preceded that and no one knows about it,
    which is possible a lot of Russian immigrated to France during the
    Revolution and subsequent Civil War, or this is the wrong
    name/mistranslation/no evidence.

42. Hrchak: No evidence of this one existing and you can look this one
    up, it's pictures of hamsters.

43. Specificists: No evidence of this one

44. Communist Populist Party

45. Swiss Social Democratic Party

46. Galician Social Democratic Party

47. German Social Democratic Party

48. Popular Freedom Party: No evidence of this one, though there is a
    modern party with a similar name, there seems to be no connection.

49. Renaissance League: This party is interesting because due to the
    Mongol invasion and subsequent trade route destruction, Russia
    didn't actually experience a "Renaissance" instead medieval style
    iconography persisted up until the Europeanization of Peter the
    Great.

50. All-Siberian Peasant Union: No evidence, could refer to any number
    of peasant uprisings.

51. Krakhalk: No evidence, possible incorrect latinization.

52. Novaia zhizn': This means New Life in Russian. Could be connected to
    the non-Menshevik Internationalists or mean something else entirely.
    Likely the Internationalists associated with Author Maxim Gorky
    though why a newspaper is on a list of political parties is beyond
    me.

53. Mesame Dasi: Georgian Social Democratic Party

54. Finnish Social Democratic Party

55. Finnish Communist Party:

\newpage

# References
